### 2021-12-08 paper/manuscript.Rmd
first paper draft

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

@@

The present study set out to validate the BRMA algorithm using a simulation study.
As a benchmark for comparison, we used restricted maximum likelihood meta-regression,
which is the standard in the field.
The algorithms are evaluated on three different criteria:
The algorithms' predictive performance in new data, 
<!-- examining its predictive performance in new data, its sensitivity and specificity in variable selection, and its bias and variance in recovering population parameters. -->
their ability to perform variable selection,
and their ability to recover population parameters.

@@

The algorithms' ability to perform variable selection was evaluated by three indices: sensitivity, specificity, and the fraction of the product over the sum (FPS).
These indices are based on proportions computed across replications within each condition.
Sensitivity $P$ is the ability to select true positives, or the probability that a variable is selected, $S = 1$, given that it has a non-zero population effect: $P = p(S = 1||\beta| >0)$.
Specificity is the ability to identify true negatives, or the probability that a variable is not selected given that it has a zero population effect: $N = p(S = 0|\beta  = 0)$.
It is possible for a poorly-fitted model to score highly on specificity by predicting all null effects while detecting no true positives.
Therefore, we additionally computed a the fraction of the product over the sum (FPS) as an overall performance criterion, which is given by $FPS=  2(\frac{P*N}{P+N})$.

@@

The simulation conditions consist of all unique combinations of the following design factors: the number of studies in the training data $k \in (22, 40, 80)$, average within-study sample size $\bar{n} \in (40, 100, 200)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of skewed normally distributed moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
The scale parameters of the skewed normal moderators were selected from $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to a standard normal distribution.
The true effect size was simulated using two models:
one with a linear effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear (cubic) effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
where $\epsilon_i \sim N(0, \tau^2)$.
The observed effect size $y_i$ was then simulated as a standardized mean difference (SMD),
sampled from a non-central t-distribution.
The design factors combined to produce `r out$conditions` unique conditions.
For all simulation conditions, 100 datasets were generated. 
<!-- x = rnorm(1000) -->
<!-- func <- function(x, b){b*x+(b*(x^2))+(b*(x^3))} -->
<!-- dat <- data.frame(x = x, -->
<!--                   y = c(func(x, .2), func(x, .5), func(x, .8)), -->
<!--                   es = rep(c(".2", ".5", ".8"), each = 1000)) -->

@@

## Predictive performance
```{r}
out <- readRDS("output.RData")
```

Results indicated that the overall $R^2_{test}$ was highest for BRMA with a Horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was not null, and by the fact that RMA had larger negative explained variance when the true effect was equal to zero (i.e., there was no effect to detect).

@@

To determine the effect of the design factors on $R^2_{test}$, ANOVA’s were performed; one per algorithm.
Note that p-values are likely not informative due to the large sample size and violation of the assumptions of normality and homoscedasticity.
The results should thus be interpreted as descriptive, not inferential, statistics.
Table \@ref(tab:tabr2eta) reports the effect size  $\eta^{2}$ of main effects and two-way interactions between simulation conditions.
As many effects of design factors were monotonously positive or negative for all algorithms,
we provide an overview of the interpretation of those effects in the Table.
Interpretation was less straightforward for a number of interactions;
for these, the median $R^2_{test}$ is graphed in Figure \@ref(fig:figanova).

```{r tabr2eta, results= "asis", eval = TRUE}
tabanova <- readRDS("anova.RData")
#tabanova$condition <- gsub("alpha", "omega", tabanova$condition, fixed = T)
#tabanova$condition <- gsub("$mean{n}$", "$n$", tabanova$condition, fixed = T)
tabanova$Factor <- gsub("\\$(omega|beta|tau)", "\\$\\\\\\1", tabanova$Factor)
tabanova$HS.vs..LASSO <- NULL
tabanova <- tabanova[, c(ncol(tabanova), 2:(ncol(tabanova)-1))]
# kbl(tabanova, caption = "Effect size of design factors and their two-way interactions on R2 the different algorithms, and of the difference between algorithms. The comparison between HS and LASSO was zero in the second decimal for all conditions. Interpretation indicates whether the effect was uniformly positive or negative (for interactions, the effect of the second design factor in the interaction) for all algorithms.", digits = 2, row.names = FALSE, escape = FALSE, booktabs = TRUE, col.names = gsub("(?<!vs)\\.", " ", names(tabanova), perl = TRUE)) |>
#   kable_styling(latex_options = c("scale_down"))
apa_table(tabanova, caption = "Effect size of design factors and their two-way interactions on R2 the different algorithms, and of the difference between algorithms. The comparison between HS and LASSO was zero in the second decimal for all conditions. Interpretation indicates whether the effect was uniformly positive or negative (for interactions, the effect of the second design factor in the interaction) for all algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabanova), perl = TRUE), longtable = TRUE)
```

```{r figanova, fig.cap="Predictive R2 for HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) for interactions. One design factor is displayed in different panels, the other on the x-axis."}
knitr::include_graphics("other_effects.png")
```

To establish difference in predictive performance between the three algorithms,
the interactions of algorithm (HS vs. LASSO, HS vs. RMA and LASSO vs. RMA) were estimated.
The $\eta^2$ of these differences between algorithms are also displayed in Table \@ref(tab:tabr2eta).
Note that $\eta^2$ for the comparison between HS and LASSO was zero in the second decimal for all conditions; thus, this comparison was omitted from the Table.
Results show that the largest differences between algorithms were due to the effect size $\beta$, number of cases in the training data $k$, and the number of irrelevant moderators $M$.
The effect of these factors by algorithm is displayed in Figure \@ref(fig:figmaindif).
Evidently, predictive performance increased most for the HS algorithm when the effect size increased above zero.
As noted previously, predictive performance of RMA was most negative (negative explained variance) when the effect size was zero.
The HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data or number of irrelevant moderators, and was relatively less affected by increases in the number of training cases (panel b) or in the number of irrelevant moderators (panel c).
Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel b).
Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators.

```{r figmaindif, fig.cap="Predictive R2 for design factors with largest differences in predictive performance across the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
knitr::include_graphics("main_diff.png")
```

@@

## Estimating residual heterogeneity
The ability of the algorithms to correctly estimate $\tau^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms. Again, the median and Mean Absolute Deviation were used as metrics for performance. The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the MetaForest algorithm $\Delta\tau^2_{Mf} = 0.09 \pm 0.13$. The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{Hs} = 0.23 \pm 0.17$. The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it. One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased. This implies that there was more variation in performance as median performance worsened.

To determine the effect of the design factors on $\Delta\tau^{2}$ for all algorithms, four separate ANOVA’s were performed. The effect size $\eta^{2}$ per condition per algorithm, including $\eta^2$ for all two-way interactions can be found in table 2. Again, the assumption of normality was violated.

The biggest predictor on the correct estimation of $\tau^{2}$ was the estimated model. This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms. Image 5A shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ . It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 6. First note the general trend that during estimation of all models $\tau^{2}$ got more overestimated as $\beta$ increased, except during estimation of the linear model, where the effect of $\beta$ on $\Delta\tau^{2}$ was close to zero, except for MetaForest. However, note the scales for the y-axes. While estimating the two-way interaction, linear and exponential model, $\Delta\tau^2$ stayed well within a confined interval. However, the algorithms severely overestimated $\tau^{2}$ when the model contained cubic terms. Especially MetaForest overestimated $\tau^{2}$ substantially when $\beta = 0.8$ and the estimated model is cubic: $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$. The other algorithms also had a $\Delta\tau^{2} > 1$ in these conditions, but the results were not as severe. Interestingly, the Pema algorithms even outperformed the RMA algorithm in these conditions.

The marginal effects of $\beta$ on $\Delta\tau^{2}$ are shown in image 5B. MetaForest was affected most by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$. The RMA algorithm performed best overall.

The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, although there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased. However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added. Image 7 shows this interaction. The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model. When the two-way interaction model was estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10. RMA performed best, followed by MetaForest. The Pema algorithms performed similarly, but worst.

The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$ was rather unnoticeable for the RMA and MetaForest algorithms. The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased. Image 5C shows the marginal relationship.

The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either. A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased which was not found for the Pema algorithms. However, A small note is that MetaForest did substantially increase in $\Delta\tau^{2}$ as more moderators were added and the estimated model is cubic. Image 8 shows the interaction between the number of moderators and the estimated model.

$\kappa$ only had a substantial effect for MetaForest; the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated. For the other algorithms, decreasing $\kappa$ had little to no effect on correctly estimating the residual heterogeneity. Image 9 shows the interaction of $\kappa$ with the estimated model.

Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 5D shows the marginal relationship.

## Variable selection
To determine the extent to which the algorithms could perform variable selection correctly, the proportion true positives [$TP$] and true negatives [$TN$] were calculated. The $TP$ and $TN$ reflect how well the algorithms accredit importance to relevant moderators and discredit importance to irrelevant moderators respectively. It should be noted that $TP$ could only take on values 1 or 0 per simulated iteration, because in all models where $\beta > 0$, only one moderator was simulated to be relevant. As $\beta$ increased, the already relevant moderator increased in relevance, rather than spreading the relevance over the other moderators. $TN$ had a bigger range and could take on values dependent on how many moderators were taken up in the model. E.g. when $\beta = 0$ and $n_{mods} = n$, $n+1$ different proportions were possible, $\frac{0}{n}$ up until $\frac{n}{n}$.

There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithms it did not matter which interval type was analyzed. It was found that MetaForest had the highest proportion true positives: $TP_{Mf} = 0.98$, closely followed by RMA: $TP_{RMA} = 0.96$. Horshoe performed slightly better than Lasso;  $TP_{Hs} = 0.91$; $TP_{Lasso} = 0.89$. As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89$. MetaForest performed worst by a large margin: $TN_{Mf} = 0.50$. The Mean Absolute Deviation for all algorithms on both $TP$ and $TN$ was 0, except for MetaForests performance on $TN$, where the Mean Absolute Deviation was 0.44.

Perfomance on $TP$ and $TN$ were very high for all algorithms, with all mean proportions, except MetaForests performance on $TN$, exceeding .89. This implies that MetaForest had issues excluding irrelevant moderators from the models. Plots were inspected to determine the effects of the design factors on the proportions. While inspecting the plots, there were found to be little marginal effects of the design factors on $TN$, while $TP$ was more affected.

Firstly, $\kappa$ only had a positive effect on $TP$. As $\kappa$ increased, $TP$ also increased. MetaForest had the highest $TP$, followed by RMA and, lastly, Horsehoe and Lasso. The increase in $TP$ for higher values of $\kappa$ was steeper for the Pema algorithms, however. There was also an interaction of $\kappa$ with the estimated model shown in image 10. During estimation of the linear and two-way interaction model, the relationship of $\kappa$ looked relatively linear. At $\kappa = 20$ the $TP$ was relatively low for the algorithms, compared to the cubic model where $TP$ starts at .98 and converges to 1 as $\kappa$ increased. This latter relationship was also found for the exponential model, although the $TP$ at $\kappa = 20$ was lower.

$\bar{n}$ had a positive and roughly linear relationship with $TP$ for all algorithms. MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst. Image 11A shows the relationship.

$\beta$ had an interaction effect with the model estimated on $TN$. Only during estimation of the two-way interaction model, $TN$ decreased as $\beta$ increased, For the other models, $TN$ remained stable. This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used. Image 12 shows the relationship. The effect of $\beta$ on $TP$ was positive; as $\beta$ increased, $TP$ increased too.

The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 11B shows the marginal relationship of $\tau^2$ on $TP$.

Finally, there was an effect of number of moderators on $TN$, but only for the two-way interaction model. The $TN$ increased as the number of moderators did. Image 13 shows the interaction. This relationship was reversed for $TP$ and was found during estimation of all models, i.e. $TP$ decreased as the number of moderators increased. Image 14 shows the relationship.

@@

>>>>

abstract: |
  Todo

keywords          : "meta-analysis, machine learning, bayesian, lasso, regularized"
wordcount         : "5356"

@@

The present study set out to validate the BRMA algorithm using a simulation study.
As a benchmark for comparison, we used restricted maximum likelihood meta-regression,
which is the standard in the field.
We evaluated the algorithms' predictive performance in new data, 
<!-- examining its predictive performance in new data, its sensitivity and specificity in variable selection, and its bias and variance in recovering population parameters. -->
<!-- their ability to perform variable selection, -->
and their ability to recover population parameters. 
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators;
under what conditions BRMA does not offer an advantage,
and which prior (horseshoe versus LASSO) is to be preferred.

@@

The algorithms' ability to perform variable selection was evaluated by sensitivity and specificity.
Sensitivity $P$ is the ability to select true positives, or the probability that a variable is selected, $S = 1$, given that it has a non-zero population effect: $P = p(S = 1||\beta| >0)$.
Specificity is the ability to identify true negatives, or the probability that a variable is not selected given that it has a zero population effect: $N = p(S = 0|\beta  = 0)$.

@@

To examine performance in a range of realistic meta-analysis scenarios,
several design factors were manipulated:
The number of studies in the training data $k \in (20, 40, 100)$, the average within-study sample size $\bar{n} \in (40, 80, 160)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
these values of $\tau^2$ fall within the range observed in practice.
Note that both BRMA and RMA assume linear effects.
To test the robustness of the algorithms to violations of this assumption, true effect sizes were simulated using two models:
one with a linear effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear (cubic) effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
where $\epsilon_i \sim N(0, \tau^2)$.
The algorithms further assume normality of residuals.
To examine robustness of the algorithms to violations of this assumption,
moderator variables were simulated as skewed normal moderators, with scale parameter $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to the standard normal distribution.
The design factors combined to produce `r out$conditions` unique conditions.
For all simulation conditions, 100 data sets were generated. 
In each data set, the observed effect size $y_i$ was simulated as a standardized mean difference (SMD),
sampled from a non-central t-distribution.

<!-- x = rnorm(1000) -->
<!-- func <- function(x, b){b*x+(b*(x^2))+(b*(x^3))} -->
<!-- dat <- data.frame(x = x, -->
<!--                   y = c(func(x, .2), func(x, .5), func(x, .8)), -->
<!--                   es = rep(c(".2", ".5", ".8"), each = 1000)) -->

@@

## Predictive performance
```{r}
out <- readRDS("output.RData")
whichhi <- prop.table(out$which_highest)
```

Within data sets, the BRMA with a horseshoe prior had the highest predictive performance `r round(whichhi[1]*100)`% of the time, followed by RMA, `r round(whichhi[3]*100)`%, and finally BRMA with a LASSO prior, `r round(whichhi[2]*100)`%.
Results indicated that the overall $R^2_{test}$ was highest for BRMA with a Horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was not null, and by the fact that RMA had larger negative explained variance when the true effect was equal to zero (i.e., there was no effect to detect).

@@

The effect of the design factors on $R^2_{test}$ was evaluated using ANOVAs.
Note that p-values are likely not informative due to the large sample size and violation of the assumptions of normality and homoscedasticity.
The results should therefore be interpreted as descriptive, not inferential, statistics.
Table \@ref(tab:tabr2eta) reports the effect size $\eta^{2}$ of simulation conditions on $R^2_{test}$.
<!-- for main effects and two-way interactions between simulation conditions. -->
<!-- , -->
<!-- we provide an overview of the interpretation of those effects in the Table. -->
<!-- For interaction effects, we report whether the interaction was spreading -->
<!-- Interpretation was less straightforward for a number of interactions; -->
<!-- for these, the median $R^2_{test}$ is graphed in Figure \@ref(fig:figanova). -->

```{r tabr2eta, results= "asis", eval = TRUE}
tabanova <- readRDS("anova.RData")
tabanova <- tabanova[!grepl(":", tabanova$condition), ]
tabanova$Interpretation[!tabanova$Interpretation %in% c("positive", "negative", "other")] <- NA
#tabanova$condition <- gsub("alpha", "omega", tabanova$condition, fixed = T)
#tabanova$condition <- gsub("$mean{n}$", "$n$", tabanova$condition, fixed = T)
tabanova$Factor <- gsub("\\$(omega|beta|tau)", "\\$\\\\\\1", tabanova$Factor)
#tabanova$HS.vs..LASSO <- NULL
tabanova <- tabanova[, c(ncol(tabanova), 2:(ncol(tabanova)-1))]
# kbl(tabanova, caption = "Effect size of design factors and their two-way interactions on R2 the different algorithms, and of the difference between algorithms. The comparison between HS and LASSO was zero in the second decimal for all conditions. Interpretation indicates whether the effect was uniformly positive or negative (for interactions, the effect of the second design factor in the interaction) for all algorithms.", digits = 2, row.names = FALSE, escape = FALSE, booktabs = TRUE, col.names = gsub("(?<!vs)\\.", " ", names(tabanova), perl = TRUE)) |>
#   kable_styling(latex_options = c("scale_down"))
#tabanova <- tabanova[!grepl(":", tabanova$condition, fixed = T), ]
apa_table(tabanova, caption = "Effect size of design factors on predictive R2 of the different algorithms, and of the difference between algorithms. Interpretation indicates whether a main effect was uniformly positive or negative across all algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabanova), perl = TRUE))#, longtable = TRUE)
# Interpretation for main effects indicates whether the effect was uniformly positive or negative or other, and for interactions, whether it is a spreading or crossover interaction.
```
```{r figr2, fig.cap="Predictive R2 for BRMA with horseshoe (HS) and LASSO prior, and RMA. Plots are sorted by largest performance difference between BRMA and RMA."}
knitr::include_graphics("r2.png")
```

```{r figanova, fig.cap="Predictive R2 for HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) for interactions. One design factor is displayed in different panels, the other on the x-axis.", eval = FALSE}
knitr::include_graphics("other_effects.png")
```

To test our research questions, we computed interactions of algorithm (HS vs. LASSO, HS vs. RMA and LASSO vs. RMA) with the other design factors.
The $\eta^2$ of these differences between algorithms are also displayed in Table \@ref(tab:tabr2eta).
Note that $\eta^2$ for the comparison between HS and LASSO was zero in the second decimal for all conditions; thus, this comparison was omitted from the Table.
The effect of design factors by algorithm is displayed in Figure \@ref(fig:figr2); these plots have been ranked from largest difference between BRMA and RMA to smallest.
Results indicate that the largest differences between algorithms were due to the effect size $\beta$, number of irrelevant moderators $M$, and the number of cases in the training data $k$.
Evidently, predictive performance increased most for the HS algorithm when the effect size increased above zero.
As noted previously, predictive performance of RMA was most negative (negative explained variance) when the effect size was zero.
The HS algorithm furthermore had the consistently highest predictive performance regardless of number of irrelevant moderators or number of cases in the training data, and was relatively less affected by increases in the number of irrelevant moderators (panel b) or in the number of training cases (panel c).
Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel c).
Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators.

```{r figmaindif, fig.cap="Predictive R2 for design factors with largest differences in predictive performance across the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms.", eval = FALSE}
knitr::include_graphics("main_diff.png")
```

@@

## Variable selection
```{r}
selprob <- out$selection
colnames(selprob) <- c("HS", "LASSO", "RMA")
truepos <- paste0(sapply(order(selprob[1,], decreasing = TRUE), function(i)paste0("$P_{", colnames(selprob)[i], "}", report(selprob[1,i]), "$")), collapse = ", ")
trueneg <- paste0(sapply(order(selprob[2,], decreasing = TRUE), function(i)paste0("$N_{", colnames(selprob)[i], "}", report(selprob[2,i]), "$")), collapse = ", ")
proboveral <- colMeans(selprob)
proboveral <- paste0(sapply(order(proboveral, decreasing = TRUE), function(i)paste0("$Acc_{", colnames(selprob)[i], "}", report(proboveral[i]), "$")), collapse = ", ")
```

To determine the extent to which the algorithms could perform variable selection correctly, the sensitivity to true positives $P$ and specificity to true negatives $N$ were calculated.
Only simulation conditions with $\beta > 0$ were used, such that the effect of the first moderator was always positive in the population and could be used to calculate $P$,
and the effect of the second moderator was always zero in the population and could be used to calculate $N$.

As the regularized algorithms shrink all coefficients towards zero, it is unsurprising that sensitivity was highest for the un-regularized algorithm RMA, followed by HS and LASSO, `r truepos`.
By contrast, specificity was higher for the regularized algorithms, `r trueneg`.
Overall accuracy reflects the trade off between sensitivity and specificity.
As the baserate of true positives and true negatives is equal in this simulation, overall accuracy is simply given by $Acc = (P+N)/2$.
Results showed that overall accuracy was approximately equal for RMA and HS, and was lower for LASSO, `r proboveral`.

Cramer's V, an effect size for categorical variables, was used to examine the effect of design factors on sensitivity (Table \@ref(tab:tabcramerp), Figure \@ref(fig:figsensitivity)) and specificity (Table \@ref(tab:tabcramern), Figure \@ref(fig:figspecificity)).
We also computed this effect size for the difference between algorithms in the number of true positives by design factor.

```{r tabcramerp, results= "asis", eval = TRUE}
tabselect <- readRDS("selected.RData")
rownames(tabselect) <- NULL
names(tabselect) <- gsub("(?<!vs)\\.", " ", names(tabselect), perl = TRUE)
apa_table(tabselect, caption = "Effect size (Cramer's V) of design factors, and of the difference between algorithms, on sensitivity (P).", digits = 2, escape = FALSE)#, longtable = TRUE)
# Interpretation for main effects indicates whether the effect was uniformly positive or negative or other, and for interactions, whether it is a spreading or crossover interaction.
```
```{r figsensitivity, fig.cap="Sensitivity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
knitr::include_graphics("sensitivity.png")
```
```{r tabcramern, results= "asis", eval = TRUE}
tabselectn <- readRDS("notselected.RData")
rownames(tabselectn) <- NULL
names(tabselectn) = gsub("(?<!vs)\\.", " ", names(tabselectn), perl = TRUE)
apa_table(tabselectn, caption = "Effect size (Cramer's V) of design factors, and of the difference between algorithms, on specificity (N).", digits = 2, escape = FALSE)#, longtable = TRUE)
```
```{r figspecificity, fig.cap="Specificity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
knitr::include_graphics("specificity.png")
```

Differences in sensitivity between the algorithms were near-zero for HS and LASSO.
The difference between the two BRMA algorithms and RMA were largest for the design factor effect size $\beta$, followed by the model and number of studies $k$.
Across all design factors, RMA had the highest sensitivity, followed by HS and then LASSO.

For specificity, differences in sensitivity between HS and LASSO were largest for the number of noise moderators $M$, followed by the effect size $\beta$, number of studies $k$, and residual heterogeneity $\tau^2$.
The difference between the two BRMA algorithms and RMA were largest for the design factor number of studies $k$, followed by the model, the number of noise moderators $M$, and the effect size $\beta$.
Across all design factors, HS had the highest specificity, followed by LASSO and then RMA.
Also note that the association between design factors and specificity was not monotonously positive or negative across algorithms.
Instead, some design factors had opposite effects for the two BRMA algorithms versus RMA.
For instance, a larger number of studies $k$ had a negative effect on specificity for the BRMA algorithms, but a positive effect for RMA - within the context that RMA had lower specificity on average.
Conversely, a greater number of noise moderators $M$ had a positive effect on specificity for BRMA, but a negative effect for RMA.

## Ability to recover population parameters

The ability to recover population parameters $\beta$ and $\tau^2$ was examined in terms of bias and variance of these estimates.
If the value of the regression coefficient as estimated by one of the algorithms is $\hat{b}$,
then the bias $B$ and variance $V$ of this estimate can be computed as the mean and variance of the difference between $\hat{b}$ and $\beta$ across simulation conditions, respectively.

Across all simulation conditions, HS had the lowest bias for $\tau^2$, $B_{HS} `r report(out[["tau2_bias"]][["hs_tau2"]])`$, 
followed by RMA, $B_{RMA} `r report(out[["tau2_bias"]][["rma_tau2"]])`$,
and then LASSO, $B_{LASSO} `r report(out[["tau2_bias"]][["lasso_tau2"]])`$.
Note that all algorithms yielded positively biased estimates. 
The LASSO estimates of $\tau^2$ had the lowest variance, $V_{LASSO} `r report(out[["tau2_variance"]][["lasso_tau2"]])`$, 
followed by HS, $V_{HS} `r report(out[["tau2_variance"]][["hs_tau2"]])`$,
and then RMA, $B_{RMA} `r report(out[["tau2_variance"]][["rma_tau2"]])`$.

The effect of the design factors on the bias in $\tau^2$ was evaluated using ANOVAs.
Table \@ref(tab:tabtau2) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{t^2}-\tau^2$.
The design factors $\beta$ and model had the largest effect on bias in estimated $\tau^{2}$ for all algorithms.
No differences between algorithms in the effect of design factors were observed.

```{r tabtau2, results= "asis", eval = TRUE}
tabtau <- readRDS("table_tau2.RData")
tabtau$Factor <- gsub("\\$(omega|beta|tau)", "\\$\\\\\\1", tabtau$Factor)
tabtau <- tabtau[, c(ncol(tabtau), 2:(ncol(tabtau)-1))]
apa_table(tabtau, caption = "Effect size of design factors on bias in tau squared for the different algorithms, and of the difference between algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabtau), perl = TRUE))
```

For the estimated regression coefficient, HS had the greatest (negative) bias across simulation conditions, $B_{HS} `r report(out[["beta_bias"]][["hs_beta1"]])`$, 
followed by LASSO, $B_{LASSO} `r report(out[["beta_bias"]][["lasso_beta1"]])`$,
and then RMA, $B_{RMA} `r report(out[["beta_bias"]][["rma_beta1"]])`$.
Note that all algorithms - including RMA - provided, on average, negatively biased estimates. 
Across simulation conditions, HS had the lowest variance, $V_{HS} `r report(out[["beta_variance"]][["hs_beta1"]])`$, 
followed by LASSO, $B_{LASSO} `r report(out[["beta_variance"]][["lasso_beta1"]])`$,
and then RMA, $B_{RMA} `r report(out[["beta_variance"]][["rma_beta1"]])`$.

The effect of the design factors on the bias in estimated $\beta$ was evaluated using ANOVAs.
Table \@ref(tab:tabbeta) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{b}-\beta$.
The skewness of moderator variables had the largest effect on bias in estimated $\beta$ for all algorithms.
Note, however, that this is likely due to the fact that the data simulated with a cubic model are analyzed with a linear model, and thus,  
was the estimated model. This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
No differences between algorithms in the effect of design factors were observed.

```{r tabbeta, results= "asis", eval = TRUE}
tabbeta <- readRDS("table_beta.RData")
tabbeta$Factor <- gsub("\\$(omega|beta|beta)", "\\$\\\\\\1", tabbeta$Factor)
tabbeta <- tabbeta[, c(ncol(tabbeta), 2:(ncol(tabbeta)-1))]
apa_table(tabbeta, caption = "Effect size of design factors on bias in beta squared for the different algorithms, and of the difference between algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabbeta), perl = TRUE))
```

@@

This simulation study validated the performance of two versions of the new BRMA algorithm, relative to state-of-the-art meta-regression (RMA).
Our analyses examined the algorithms' predictive performance, which is a measure of generalizability,
their ability to perform variable selection,
and their ability to recover population parameters.
Our research questions were whether BRMA offers a performance advantage over RMA in terms of any of these indicators;
under what conditions BRMA does not offer an advantage,
and which prior (horseshoe versus LASSO) is to be preferred.

Results indicated that the BRMA algorithms had higher predictive performance than RMA in the presence of relevant moderators.
In the absence of relevant moderators, RMA produced overfit models; in other words, its models generalized poorly to new data.
The predictive performance of the BRMA algorithms also suffered less than that of RMA in the presence of more irrelevant moderators.
The BRMA algorithms were also more efficient, in the sense that they achieved greater predictive performance when the number of studies in the training data was low.
Across all conditions, BRMA with a horseshoe prior achieved the highest average predictive performance, and within each data set, BRMA with a horseshoe prior most often had the best predictive performance (in `r round(whichhi[1]*100)`% of replications).
This provides strong evidence that BRMA with a horseshoe prior is generally preferable when the goal is to obtain findings that generalize to new data.

With regard to variable selection, results indicated that the penalized BRMA algorithms had lower sensitivity: they were less able to select relevant moderators than the un-penalized RMA algorithm.
Conversely, the BRMA algorithms had better specificity: they were better able to reject irrelevant moderators than RMA.
These results are unsurprising because the BRMA algorithms shrink all regression coefficients towards zero.
This diminishes their ability to detect true effects and aids their ability to reject irrelevant moderators.
Importantly, the overall accuracy was approximately equal for RMA and BRMA with a horseshoe prior.
This means that the total number of Type I and Type II errors will be approximately the same when choosing between these two methods - but there is a tradeoff between sensitivity and specificity.
Applied researchers must consider whether sensitivity or specificity is more important in the context of their research.
When meta-analyzing a heterogeneous body of literature, with many between-study differences that could be coded as moderators, BRMA may be preferred due to its greater ability to retain only relevant moderators.
Conversely, when meta-analyzing a highly curated body of literature with a small number of theoretically relevant moderators, un-penalized RMA might be preferred.

With regard to the algorithms' ability to recover population effect sizes of moderators,
we observed that BRMA with a horseshoe prior had the greatest bias towards zero across simulation conditions, followed by LASSO, and then RMA.
Note that all algorithms provided, on average, negatively biased estimated.
The variance of the estimates followed the opposite pattern.
This unsurprising result illustrates the bias-variance trade-off in penalized regression.
The greater predictive performance of the BRMA algorithms is a direct consequence off this trade-off.
